---
title: "Exercise: Explore, Clean, and Wrangle Data"
author: "Taylor"
format: html
---

## About the data

This data set contains information on the abundance, size, and fishing pressure of California spiny lobster along the mainland coast of the Santa Barbara Channel. The data set can be found at [this link](Exercise: Explore, Clean, and Wrangle Data). Data was accessd on 6/29/2023.

## Setup
Load libraries

```{r}
library(readr)
library(dplyr)
library(ggplot2)
library(tidyr)
```



## Read and explore data

```{r}
lobster_abundance <- read_csv("https://portal.edirepository.org/nis/dataviewer?packageid=knb-lter-sbc.77.8&entityid=f32823fba432f58f66c06b589b7efac6")

lobster_traps <- read_csv("https://portal.edirepository.org/nis/dataviewer?packageid=knb-lter-sbc.77.8&entityid=66dd61c75bda17c23a3bce458c56ed84")


summary(lobster_abundance)
head(lobster_abundance)
summary(lobster_traps)
head(lobster_traps)
```


## Exercise 1


```{r}
#unique(lobster_abundance$SIZE_MM)
lobster_abundance <- lobster_abundance %>% 
  mutate(SIZE_MM = na_if(SIZE_MM, -99999))
unique(lobster_abundance$SIZE_MM)
```



## Exercise 2

```{r}
AQUE_70_plus <- lobster_abundance %>% 
  filter(SITE == "AQUE",
         SIZE_MM > 70)
AQUE_70_plus
```



## Exercise 3

## Exercise 4

## Exercise 5

## Exercise 6
